Pillar 1 - Sequential Pattern Mining

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
save SR

### Save Sequences Rules

@@

We save and remove objects:
```{r saving and rm SR}
#Saving sequence rules
save(
    SR,
    SR_TPF,
    #SR_expanded_Grade,
    file = "App/SR.RDATA")

#clean unnecessary objects
# rm(clean_SR, my_SR, 
#    sequences,
#    #sequences_expanded_Grade,
#    n_students,
#    SR_taken, SR_PF, SR_HL, SR_G,
#    SR_TPF
#    #SR_expanded_Grade
#    )
```

>>>>

### Save Sequences Rules
```{r}
#
# Save Sequence rules
save(
  SR,
  file = "App/SR.RDATA"
)

# Remove objects
rm(
  my_cspade, my_ruleInduction, clean_rules, compute_rhs.support, edit_rules, make_SR,
  SR, sequences
)
```

@@
